### 2021-02-09 SupplementaryMaterial/Acknowledgments.tex
update

% Place acknowledgments below.
%First of all, I would like to thank my advisor Prof. Dinghao Wu for the continuous support of my Ph.D. study. I had a very hard time during the pandemic. Without his encouragement and support, I could not have finished the program. I also thank Dinghao for inviting me to Switzerland during his sabbatical leave. A large portion of the research presented in the dissertation was finished when I worked in Switzerland. The knowledge and skills I learned from him will also help me make progress in my future career.

%Beside my advisor, I would like to thank my committee members, Prof. Peng Liu, Prof. Sencun Zhu, Prof. Benjamin Hanrahan, and Prof. James R. Larus for their time, reviewing my dissertation.

%I would also like to thank Dr. Kang Li, Mr. Zhaofeng Chen, Dr. Mingshen Sun, Dr. Greg Zaverucha and Dr. Brian LaMacchia for their help during my internship at Baidu X-Lab and Microsoft Research Lab.  I also thank my friends and collaborators at Penn State University and EPFL.

%This research was supported in part by by the National Science Foundation (NSF) under grant CNS-1652790, and the Office of Naval Research (ONR) under grants N00014-16-1-2912, N00014-16-1-2265, and N00014-17-1-2894.

%Any opinions, conclusions in the paper do not reflect the views of funding agencies.

\bibliographystyle{IEEEtran}
\bibliography{refs}

%\newpage
%\clearpage
%\appendices
%\setcounter{section}{0}
%\section*{Supplementary Materials to Submission \#63}
%\setcounter{section}{1}
%\setcounter{page}{1}
%\input{sections/appendix}

\end{document}

>>>>

% Place acknowledgments below.
First of all, I would like to thank my advisor Prof. Dinghao Wu for the continuous support of my Ph.D. study. I had a very hard time during the pandemic. Without his encouragement and support, I could not have finished the program. I also thank Dinghao for inviting me to Switzerland during his sabbatical leave. A large portion of the research presented in the dissertation was finished when I worked in Switzerland. The knowledge and skills I learned from him will also help me make progress in my future career.

Beside my advisor, I would like to thank my committee members, Prof. Peng Liu, Prof. Sencun Zhu, Prof. Benjamin Hanrahan, and Prof. James R. Larus for their time, reviewing my dissertation.

I would also like to thank Dr. Kang Li, Mr. Zhaofeng Chen, Dr. Mingshen Sun, Dr. Greg Zaverucha and Dr. Brian LaMacchia for their help during my internship at Baidu X-Lab and Microsoft Research Lab.  I also thank my friends and collaborators at Penn State University and EPFL.

This research was supported in part by by the National Science Foundation (NSF) under grant CNS-1652790, and the Office of Naval Research (ONR) under grants N00014-16-1-2912, N00014-16-1-2265, and N00014-17-1-2894. Any opinions, conclusions in the paper do not reflect the views of funding agencies.
